### 2020-10-12 README.Rmd
adjust figure path
The visualize output in the README has a bad path on the websites.
link to image file in readme

```{r, message = FALSE, warning = FALSE}
visualize(null_distn) +
  shade_p_value(obs_stat = F_hat, direction = "greater")
```

>>>>

```{r viz, message = FALSE, warning = FALSE, eval = FALSE}
visualize(null_distn) +
  shade_p_value(obs_stat = F_hat, direction = "greater")
```

```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/README_files/figure-gfm/viz-1.png")
```
